Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2015-07-14 Papers/InProgress/HajekAndersonControversy/main.tex
Move definition of independency from footnotes to main text.

Nevertheless, \citet[p.~7]{Hajek2002} acknowledges Anderson's rebuttal,
and apparently accepts it, as evidenced by his use\footnote{
  A4 and A5 are used by \citet[p.~11]{Hajek2002} in,
  respectively, Lemma 4 and Theorem 4.
}
of A4 and A5', as well as varying domain semantics, in his new
emendation (named \AOEH \citep[sec.~4]{Hajek2002}, cf. Fig.
\ref{fig:Hajek1}), which replaces Anderson's A:A1 and A2 by a simpler
axiom H:A12. Surprisingly, the computer-assisted formalization of
\AOEH\ shows that A4 and A5' are still superfluous. Moreover,
A4 and A5' are independent\footnote{
  An axiom $A$ is \emph{independent} of a set of axioms $S$ iff
  there are models of $S$ where $A$ is true and other models of
  $S$ where $A$ if false.
}
of the other axioms and definitions.
Therefore, A4 and A5' are not redundant, despite their superfluousness.

>>>>

Nevertheless, \citet[p.~7]{Hajek2002} acknowledges Anderson's rebuttal,
and apparently accepts it, as evidenced by his use\footnote{
  A4 and A5 are used by \citet[p.~11]{Hajek2002} in,
  respectively, Lemma 4 and Theorem 4.
}
of A4 and A5', as well as varying domain semantics, in his new
emendation (named \AOEH \citep[sec.~4]{Hajek2002}, cf. Fig.
\ref{fig:Hajek1}), which replaces Anderson's A:A1 and A2 by a simpler
axiom H:A12. Surprisingly, the computer-assisted formalization of
\AOEH\ shows that A4 and A5' are still superfluous. Moreover,
A4 and A5' are independent
of the other axioms and definitions.
Therefore, A4 and A5' are not redundant, despite their superfluousness.

\begin{definition}
  An axiom $A$ is \emph{independent} of a set of axioms $S$ iff
  there are models of $S$ where $A$ is true and other models of
  $S$ where $A$ if false.
\end{definition}
